---
title: "Data visualization"
description: |
  R for Data Science Book
author:
  - name: Alexis Solis Cancino
    url: https://www.linkedin.com/in/asolisc/
    # affiliation: Spacely Sprockets
    # affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true

    css: "styles.css"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE)

source("D:/01-Data-Science/03-Helper-Scripts/ggplot2_themes.R")
# file.show("D:/01-Data-Science/03-Helper-Scripts/ggplot2_themes.R")

library(ggplot2)

```

# 1. Introduction

The `ggplot2` package is one of the most versatile frameworks for data visualization. It implements the **grammar of graphics** - a system for describing and building graphs by using *layers*. This package is one of the 8 *core-tidyverse* packages.

# 2. First Steps

We first start by loading the `tidyverse` meta-package:

```{r}
library(tidyverse)
```

Then, we can use the `mpg` tibble, a dataset included in the `ggplot2` package. `mpg`contains observations collected by the US Environmental Protection Agency on 38 models of car.

```{r}
mpg
```

```{r, layout = "l-body-outset", fig.asp=0.618}
mpg %>% 
  mutate(cyl = as_factor(cyl)) %>% 
  ggplot(mapping = aes(x = displ, y = hwy, colour = cyl)) +
  geom_point() +
  scale_colour_manual(values = amazing_colors)
```

# 3. Aesthetic Mappings

You can add a third variable, like class, to a two dimensional scatterplot by mapping it to an aesthetic. An aesthetic is a visual property of the objects in your plot.

Since we already use the word "value" to describe data, let's use the word "level" to describe aesthetic properties.

```{r}
mpg %>%
  ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

To map an aesthetic to a variable, associate the name of the aesthetic to the name of the variable inside `aes()`. ggplot2 will automatically assign a unique level of the aesthetic (here a unique color) to each unique value of the variable, a process known as scaling.

```{r}
mpg %>%
  ggplot() +
  geom_point(mapping = aes(x = displ, 
                           y = hwy, 
                           size = class,
                           colour = class))
```

We could also use the `alpha` or `shape` aesthetic:

```{r}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, 
                 y = hwy,
                 alpha = class))
```

```{r}
mpg %>% 
  ggplot(aes(x = displ, y = hwy)) +
  geom_point(aes(shape = class))
```

What happened to the SUVs? ggplot2 will only use six shapes at a time. By default, additional groups will go unplotted when you use the shape aesthetic.

It selects a reasonable scale to use with the aesthetic, and it constructs a legend that explains the mapping between levels and values. For x and y aesthetics, ggplot2 does not create a legend, but it creates an axis line with tick marks and a label. The axis line acts as a legend; it explains the mapping between locations and values.

You can also set the aesthetic properties of your geom manually. For example, we can make all of the points in our plot blue:

```{r}
mpg %>% 
  ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy), 
             colour = "dark green")
```

To set an aesthetic manually, set the aesthetic by name as an argument of your geom function; i.e. it goes outside of `aes()`.

## 3.1 Exercises

1.  What's gone wrong with this code? Why are the points not blue?

```{r}
mpg %>% 
  ggplot() +
  geom_point(mapping = aes(x = displ,
                           y = hwy,
                           color = "blue"))
```

The color should be set outside the `aes()` function, i.e. as an argument to the `geom()` function.

2.  Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run `mpg`?

```{r, eval=FALSE}
# Not run
help(mpg)
```

```{r}
mpg %>% glimpse()
```

The categorical variables are:

-   `manufacturer`

-   `model`

-   `trans`

-   `drv`

-   `fl`

-   `class`

The numeric variables are:

-   `model`

-   `year`

-   `cyl`

-   `cty`

-   `hwy`

3.  Map a continuous variable to `color`, `size`, and `shape`. How do these aesthetics behave differently for categorical vs. continuous variables?

```{r}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, y = hwy, color = year))
```

```{r}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, y = hwy, size = year))
```

```{r, eval = F}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, y = hwy, shape = year))
```

The `color`, `shape`, and `size` aesthetics work better with categorical variables. `shape` levels cannot be mapped to a continuous variable.

4.  What happens if you map the same variable to multiple aesthetics?

```{r}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, 
                 y = hwy, 
                 color = class, 
                 alpha = class))
```

`ggplot2` maps them all accordingly.

5.  What does the stroke aesthetic do? What shapes does it work with? (Hint: use `?geom_point`).

```{r}
mpg %>%
  ggplot() +
  geom_point(aes(x = displ,
                 y = hwy,
                 color = class),
             stroke = 2,
             shape = 11)
```

`stroke` changes the border's width of certain shapes. For example, shapes 11 and 21 work with stroke. `stroke` is not available for all `geom()` functions.

6.  What happens if you map an aesthetic to something other than a variable name, like `aes(colour = displ < 5)`? Note, you'll also need to specify `x` and `y`.

```{r}
mpg %>% 
  ggplot() +
  geom_point(mapping = aes(x = displ,
                           y = hwy,
                           colour = displ < 5))
```

## 4. Common Problems

One common problem when creating ggplot2 graphics is to put the `+` in the wrong place: it has to come at the end of the line, not the start. So, for example, the following code is wrong:

```{r wrong-code, eval = FALSE}
ggplot(data = mpg) 
+ geom_point(mapping = aes(x = displ, y = hwy))
```

## 5. Facets

Another way to add additional variables, particularly useful for categorical variables, is to split your plot into **facets**: subplots that each display one subset of the data.

### Facet by One Variable

To facet your plot by a single variable, use `facet_wrap()`. The first argument of `facet_wrap()` should be a formula created with `~` followed by a variable name. The variable that you pass to `facet_wrap()` *should be discrete*.

```{r}
mpg %>% 
  ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

### Facet by Two Variables

To facet your plot on the combination of two variables, add `facet_grid()` to your plot call. The first argument of `facet_grid()` is also a formula. This time the formula should contain two variable names separated by a `~`. For example: `x ~ y`. We can facet the `mpg` dataset by `drv` and `cyl`:

```{r}
mpg %>% 
  ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```

### Facet: Rows Only

If you prefer to not facet in the rows or columns dimension, use a `.` instead of a variable name. Thus, to facet by rows only use: `+ facet_grid(var1 ~ .)`.

```{r}
mpg %>% 
  ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(cyl ~ .)
```

### Facet: Columns Only

To facet by columns only use: `+ facet_grid(. ~ var1)`.

```{r}
mpg %>% 
  ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

## 5.1 Exercises

1.  What happens if you facet on a continuous variable?

```{r}
mpg %>% 
  ggplot(aes(x = displ, y = hwy)) +
  geom_point() +
  facet_grid(year ~ cty)
```

It either displays too many facets or groups them. This happens because the continuous variable is converted to categorical.

2.  What do the empty cells in plot with `facet_grid(drv ~ cyl)` mean? How do they relate to this plot?

```{r}
mpg %>% 
  ggplot(aes(displ, hwy)) +
  geom_point() +
  facet_grid(drv ~ cyl)
```

Empty cells mean that there's no data that meets the criteria for that specific facet. In this example, it means that there are no 4- and 5-cylinder cars with rear-wheel-drive.

3.  What plots does the following code make? What does `.` do?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

It plots the data into facets according to the variable `drv` and `cyl`, respectively. The `.` argument inside `facet_grid` indicates you're faceting by only one variable.

4.  Take the first faceted plot in this section:

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

What are the advantages to using faceting instead of the color aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

Faceting actually divides the data into panels, so the separation of the categorical variable is more visual and clear. On the other hand, if the *factor* (categorical) variable had too many different categories, faceting wouldn't be feasible, since we would have too many panels and it's no longer practical to visualize. That's were the `color` aesthetic could work a little bit better.

5.  Read `?facet_wrap`. What does `nrow` do? What does `ncol` do? What other options control the layout of the individual panels? Why doesn't facet\_grid() have `nrow` and `ncol` arguments?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2, dir = "v")
```

The `nrow` and `ncol` arguments are unnecessary for `facet_grid()` since the number of unique values of the variables specified in the function determines the number of rows and columns.

6.  When using `facet_grid()` you should usually put the variable with more unique levels in the columns. Why?

There will be more space for columns if the plot is laid out horizontally (landscape).

## 6. Geometric Objects

In ggplot2 syntax, there exist different **geoms**. A **geom** is the geometrical object that a plot uses to represent data. To use *geoms* you'll have to use a family of functions specified by: `geom_*()`.

For example, bar charts use `geom_bar`, line charts use `geom_line()`, boxplots use `geom_boxplot()`, and so on. Scatterplots break the trend, as they are called by using the `geom_point()` *geom*. Below are a couple of examples:

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ)) +
  geom_boxplot(
    fill = amazing_colors[10]) + 
  scale_y_continuous(
    limits = c(-2.5,2.5)
  ) +
  labs(
    title = "Just a boxplot geom"
  )
```

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ)) +
  geom_bar(fill = amazing_colors[8]) +
  labs(
    title = "This is a geom_bar() plot"
  )
```

Every geom function in ggplot2 takes a `mapping` argument. However, not every aesthetic works with every geom. You could set the shape of a point, but you couldn't set the "shape" of a line. On the other hand, you *could* set the `linetype` of a line. An interesting example is the `geom_smooth()` geom, which will assign a different `linetype` and a different line for each unique value of the variable that you're mapping to it.

```{r}
mpg %>% 
  ggplot() +
  geom_smooth(
    
    # Map the aesthetics
    mapping = aes(x = displ, 
                  y = hwy, 
                  linetype = drv,
                  color = drv),
    
    # Omit the confidence interval
    se = FALSE) +
  scale_color_manual(values = amazing_colors)
```

To better understand what `geom_smooth()` is doing, we can overlay the line on top of the raw data and color everything according to `drv`.

```{r}
mpg %>% 
  
  # Setting "global" aesthetics
  ggplot(aes(x = displ, y = hwy, color = drv)) +
  
  # scatterplot geom goes first
  geom_point() +
  
  # geom_smooth goes "on top" of scatterplot
  geom_smooth(se = FALSE) +
  
  # Choosing the colors manually
  scale_color_manual(values = amazing_colors)
```

### Cheatsheet

`ggplot2` provides over 40 geoms, and [extension packages](https://exts.ggplot2.tidyverse.org/gallery/) provide even more. The best way to get a comprehensive overview is the [`ggplot2` cheatsheet](%5Bhttps://rstudio.com/resources/%5D(https://rstudio.com/resources/cheatsheets/)).

### The `group` aesthetic

Most *geoms* use a single geometric object (e.g. a line) to display multiple rows of data. If you'd like to display **several objects** to map categorical variables to the geometric objects, you can use the `group` aesthetic.

Actually, `ggplot2` will use the `group` aesthetic when you map categorical variables to any aesthetic, but the convenient feature of `group` is that it doesn't add a legend or distinguish features to the *geoms*.

For example, see the difference between the following plots:

```{r}
library(cowplot)

plot1 <- mpg %>% 
  ggplot() +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv),
              se = FALSE) +
  scale_color_manual(values = amazing_colors)

plot2 <- mpg %>% 
  ggplot() +
  geom_smooth(mapping = aes(x = displ, y = hwy, colour = drv),
              se = FALSE) +
  theme(legend.position = "bottom") +
  scale_color_manual(values = amazing_colors)

cowplot::plot_grid(plot1, plot2, nrow = 2)
```

### Legend display with `show.legend`

If we'd like to delete the legend for the second plot, we can actually add `show.legend = FALSE`:

```{r}
mpg %>% 
  ggplot() +
  geom_smooth(mapping = aes(x = displ, y = hwy, colour = drv),
              se = FALSE,
              show.legend = FALSE)
```

### Multiple geoms

To add multiple *geoms* in the same plot, simply add multiple `geom_*()` functions to `ggplot()`:

```{r}
mpg %>% 
  ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy),
             colour = amazing_colors[3]) +
  geom_smooth(mapping = aes(x = displ, y = hwy),
              colour = amazing_colors[2])
```

### Setting *global* mappings

The code above involved some repetition on the variable mapping. If you wanted to change the mapping, say, of the *y-axis variable*, then it you'd have to change it in both `geom_*()` functions. To avoid this, you can set a global mapping by setting the `mapping = aes()` function inside the `ggplot()` call:

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, y = hwy)) +
  geom_point(colour = amazing_colors[5]) +
  geom_smooth(colour = amazing_colors[4])
```

### Local mappings

Placing a mapping inside a `geom_*()` function will treat it as a local mapping for that layer. It will overwrite the global mappings set *for that layer only*. This makes it possible to display different aesthetics in different layers:

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(colour = class)) +
  geom_smooth() +
  scale_colour_manual(values = amazing_colors)
```

### Local Data

You can use the same idea to display *different data on each geom or layer.* In the example below, the smooth line display just a subset of the `mpg` dataset. The *local* `data` argument in `geom_smooth()` overrides the global data argument in `ggplot()` for that layer only:

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(colour = class)) +
  geom_smooth(
    
    # Filter the data for "suv" class
    data = mpg %>% filter(class == "suv"),
    
    se   = FALSE,
    color = amazing_colors[4]
  ) +
  scale_colour_manual(values = amazing_colors)
```

```{r}
mpg %>% select(class)
```

## 6.1 Exercises

1.  What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

For the line chart, you would use `geom_line()`:

```{r}
tidyquant::FANG %>% 
  filter(symbol == "FB") %>% 
  ggplot(mapping = aes(x = date, y = close)) +
  geom_line(color = amazing_colors[3])
```

For the boxplot, you would use `geom_boxplot()`:

```{r}
tidyquant::FANG %>% 
  ggplot(mapping = aes(x = symbol, y = close)) +
  geom_boxplot(aes(fill = symbol)) +
  scale_fill_manual(values = amazing_colors[2:6])
```

For a histogram, you would use `geom_histogram()`:

```{r}
tidyquant::FANG %>% 
  filter(symbol == "AMZN") %>% 
  ggplot(mapping = aes(x = close)) +
  geom_histogram(fill = amazing_colors[3], 
                 colour = amazing_colors[1], 
                 bins = 15)
```

For an area chart, you would use `geom_area()`:

```{r}
tidyquant::FANG %>% 
  filter(symbol == "AMZN") %>% 
  ggplot(mapping = aes(x = date, y = close)) +
  geom_area(fill = amazing_colors[5])
```

2.  Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

3.  What does `show.legend = FALSE` do? What happens if you remove it? Why do you think I used it earlier in the chapter?

It removes the legend that is produced by a certain `geom_*()` function.

4.  What does the `se` argument to `geom_smooth()` do?

The documentation says that it is used to choose if the *confidence interval* should be computed and displayed (or not, when it's set to `FALSE`).

5.  Will these two graphs look different? Why/why not?

```{r, eval = FALSE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```

No they won't they have the exact same mappings and data. The only difference is that the first code uses *global* data and mappings, while the second chunk uses *local* data and mappings.

6.  Recreate some graphs:

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, hwy)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, hwy)) +
  geom_point() +
  geom_smooth(mapping = aes(group = drv),
              se = FALSE)
```

```{r}
mpg %>% 
  
  # Color is mapped in both geoms, so we can set it globally
  ggplot(mapping = aes(x = displ, y = hwy, colour = drv)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_color_manual(values = amazing_colors)
```

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, y = hwy)) +
  
  # Color is only mapped in the geom_point() geom
  geom_point(mapping = aes(colour = drv)) +
  geom_smooth(se = FALSE) +
  scale_color_manual(values = amazing_colors)
```

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(linetype = drv),
              se = FALSE) +
  geom_point(mapping = aes(colour = drv)) +
  scale_color_manual(values = amazing_colors[2:4])
```

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, y = hwy, colour = drv)) +
  
  # The trick is to use two geom_point() geoms
  geom_point(colour = "white", size = 5) +
  geom_point() +
  scale_color_manual(values = amazing_colors[2:4]) +
  theme(
    plot.background = element_rect(fill = "#F4F3EE")
  )
panel.background = element_line(colour = "#F4F3EE")
```

## 7.Statistical Transformations

For this section, the `diamonds` dataset that comes in `ggplot2` is used. It contains information about \~54,000 diamonds, including the `price`, `carat`, `color`, `clarity`, and `cut` of each diamond.

On the following chart, the *x-axis* displays `cut` while the *y-axis* displays the `count` variable. However, the `count` variable **is not present in the data**.

```{r}
diamonds %>% 
  ggplot() +
  geom_bar(mapping = aes(x = cut))
```

Where does count come from? Many graphs -- like scatterplots -- plot the raw values of your dataset. Other graphs, like bar charts, calculate new values to plot:

-   bar charts, histograms, and frequency polygons bin your data and then plot bin counts, the number of points that fall in each bin.

-   smoothers fit a model to your data and then plot predictions from the model.

-   boxplots compute a robust summary of the distribution and then display a specially formatted box.

## 7.1 What is a *stat*

The algorithm that these plots use to calculate new values from existing data is called a **stat** -- which is short for *statistical transformations*. A *stat* is a function that **builds new variables to be plotted**.

### Which stat is used

You can learn which stat a geom uses by inspecting the default value for the `stat` argument. For example, `?geom_bar` shows that the default value for `stat` is `stat = "count"`, which means that `geom_bar()` uses `stat_count()`. The documentation for `?geom_bar` also shows a section for *Computed variables* which details the variables that are computed by the `stat_count()` function -- in this case, `count` and `prop`.

### Using geoms or stats

You can *generally* use *geoms* and *stats* **interchangeably**. For example, you can recreate the above chart with a `stat_count()` call:

```{r}
diamonds %>% 
  ggplot() +
  stat_count(mapping = aes(x = cut))
```

This works because every geom has a default stat; and every stat has a default geom. This means that you can typically use geoms without worrying about the underlying statistical transformation. There are three reasons you might need to use a *stat* explicitly:

1.  **Overriding the default stat**: using a different-than-default *stat* could be useful because it allows you to map a different metrics to the *y-axis*. For example, one can change the default `stat_count` in a `geom_bar()` *geom* and use the `stat_identity()` *stat* to map the *y-axis* height to the values of a *y-variable* specified in the `aes()` function. You may want to do this if you had other kind of *frequencies* already present in your data. For example:

```{r}
tribble(
  ~cut,         ~freq,
  "Fair",       1610,
  "Good",       4906,
  "Very Good",  12082,
  "Premium",    13791,
  "Ideal",      21551
) %>% 
  
  # Create a relative frequency column
  mutate(rel_freq = freq / sum(freq)) %>% 
  
  ggplot(mapping = aes(x = cut, y = rel_freq)) +
  
  # Map the y-axis to the rel_freq column
  geom_bar(stat = "identity")
```

2.  **Using *stats* as *aesthetics***: it could be useful to map certain *stats* to the `aes()` function. You could choose between the *Computed variables* section in the *help* section. The following is a nifty, little trick to plot a relative frequency plot:

```{r}
diamonds %>% 
  ggplot() +
  geom_bar(
    mapping = aes(x = cut, 
                  
                  # We map the stat "groupwise proportion" to the y-axis
                  y = stat(prop), 
                  
                  # Why do we need this aesthetic?????
                  group = 1)
  )
```

3.  **Getting more out of statistical transformations**: the best example is getting a *3-number-summary* of your data with the `stat_summary()` *stat*.

```{r}
diamonds %>% 
  ggplot(mapping = aes(x = cut, y = depth)) +
  stat_summary(
    fun.min = min,
    fun.max = max,
    fun = median
  )
```

## 7.2 Exercises

1.  What is the default geom associated with `stat_summary()`? How could you rewrite the previous plot to use that geom function instead of the stat function?

    The *geom* used appears to be `pointrange`. The following code produces the same plot as before:

```{r}
diamonds %>% 
  ggplot(mapping = aes(x = cut, y = depth)) +
  geom_pointrange(
      stat = "summary",
      fun = median,
      fun.min = min,
      fun.max = max
  )
```

The default stat for `geom_pointrange()` is `identity()` but we can add the argument `stat = "summary"` to use `stat_summary()` instead of `stat_identity()`.

2.  What does `geom_col()` do? How is it different to `geom_bar()`?

`geom_col()` will represent values of the data in the *y-axis*, so it's similar to using `geom_bar(stat = "identity")`. On the other hand, `geom_bar()` makes the height of the bars proportional to the number of cases of each categorical variable (i.e. it *counts* them).

Another difference is that `geom_col()`'s default *stat* is `stat_identity()`, which leaves the data as is; while `geom_bar()`'s default *stat* is `stat_count()`, which counts the data.

3.  Most geoms and stats come in pairs that are almost always used in concert. Read through the documentation and make a list of all the pairs. What do they have in common?


4. What variables does `stat_smooth()` compute? What parameters control its behavior?

`stat_smooth()` computes...

The parameters for `stat_smooth()` are:


5.  In our proportion bar chart, we need to set `group = 1`. Why? In other words what is the problem with these two graphs?

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = after_stat(prop)))
```


```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = after_stat(prop)))
```

## 8.Position Adjustments

## 9.Coordinate Systems

## 10.The layered grammar of graphics
