---
title: "5 Data Transformation"
description: |
  R for Data Science Book
author:
  - name: Alexis Solis
    url: alexis.solisc@gmail.com
    # affiliation: Spacely Sprockets
    # affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 2
    css: "styles.css"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE)

source("D:/01-Data-Science/03-Helper-Scripts/ggplot2_themes.R")
```

# 5.1 Introduction

This chapter is all about data wrangling.

```{r}
library(tidyverse)
library(tidyquant)
library(nycflights13)
```

## 5.2 Filter rows with `filter()`

`filter()` allows you to choose rows based on a set of logical conditions.

```{r}
FANG %>% 
  filter(symbol == "FB")
```

### 5.2.1 Comparisons

```{r}
sqrt(2) ^ 2 == 2
1 / 49 * 49 == 1
```

```{r}
near(sqrt(2) ^ 2,  2)
near(1 / 49 * 49, 1)
```

### 5.2.2 Logical operators

```{r}
FANG %>% 
  filter(symbol == "FB" | symbol == "GOOG")
```

We could also use the `value matching` operator: `%in%` as in: `x %in% y`. This will select every row where `x` is one of the values in `y`.

```{r}
FANG %>% 
  filter(symbol %in% c("FB", "GOOG"))
```

As well as `&`and `|`, R also has `&&` and `||`. Don't use them here! You'll learn when you should use them in conditional execution.

### 5.2.3 Missing values

If you want to determine if a value is missing, use `is.na()`.

`filter()` only includes rows where the condition is TRUE; it excludes both FALSE and NA values. If you want to preserve missing values, ask for them explicitly:

```{r}
df <- tibble(x = c(1, NA, 3))

df %>% 
  filter(x > 1)

df %>% 
  filter(is.na(x) | x > 1)
```

## 5.2.4 Exercises

1.  Find all flights that:

-   Had an arrival delay of two or more hours.

```{r}
flights %>% 
  filter(arr_delay >= 120)
```

-   Flew to Houston (`IAH` or `HOU`)

```{r}
flights %>% 
  filter(dest == "IAH" | dest == "HOU")
```

Another options we have is to use the *value matching operator* `%in%`

```{r}
flights %>% 
  filter(dest %in% c("IAH", "HOU"))
```

-   Were operated by United, American, or Delta.

We first print the `airlines` tibble to see the names and their abbreviations:

```{r}
airlines
```

We see that: DL = Delta Air Lines Inc. ; UA = United Air Lines Inc.; AA = American Airlines Inc.

```{r}
flights %>% 
  filter(carrier %in% c("DL", "UA", "AA")) %>% 
  relocate(carrier, .after = year)
```

-   Departed in summer (July, August, and September).

```{r}
flights %>% 
  filter(month %in% c(7, 8, 9))
```

-   Arrived more than two hours late, but didn't leave late.

```{r}
flights %>% 
  filter(dep_delay <= 0, arr_delay >= 120)
```

-   Were delayed by at least an hour, but made up over 30 minutes in flight

```{r}
flights %>% 
  filter(dep_delay >= 60, dep_delay - arr_delay > 30)
```

-   Departed between midnight and 6am (inclusive)

```{r}
flights %>% 
  filter(dep_time <= 600 | dep_time == 2400)
```


2.  Another useful `dplyr` filtering helper is `between()`. What does it do? Can you use it to simplify the code needed to answer the previous challenges?

`between()` is the equivalent to the `BETWEEN` clause in `SQL`. In `dplyr` it has three main arguments: a numeric vector of values (`x`), a lower boundary (`left`) and an upper boundary (`right`). It returns `TRUE` if the numeric vector falls in the range specified by the boundaries.

Let's use the function to simlify some previous exercises:

- Find flights that departed in summer (July, August, and September)

```{r}
flights %>%
  filter(
    between(x = month, 
            left = 7, 
            right = 9)
    )
```


