---
title: "11 Data import"
description: |
  R for Data Science Book
author:
  - name: Alexis Solis Cancino
    url: https://www.linkedin.com/in/asolisc/
    # affiliation: Spacely Sprockets
    # affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    css: "styles.css"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE)

source("D:/01-Data-Science/03-Helper-Scripts/ggplot2_themes.R")
# file.show("D:/01-Data-Science/03-Helper-Scripts/ggplot2_themes.R")

library(tidyverse)
library(here)
library(glue)
library(hms)

options(ggplot2.continuous.colour="viridis")
options(ggplot2.continuous.fill="viridis")
```

# 11.1 Introduction

wdwdw

```{r}
x
```

### 11.3.4 Dates, date-times, and times

### Exercises

1.  What are the most important arguments to `locale()`?

```{r}
parse_date(x = , locale = )
```

We list the most important ones (and their default) below:

-   `date_names` = "en",
-   `date_format` = "%AD",
-   `time_format` = "%AT",
-   `decimal_mark` = ".",
-   `grouping_mark` = ",",
-   `tz` = "UTC",
-   `encoding` = "UTF-8",
-   `asciify` = FALSE

2.  What happens if you try and set `decimal_mark` and `grouping_mark` to the same character? What happens to the default value of `grouping_mark` when you set `decimal_mark` to ","? What happens to the default value of `decimal_mark` when you set the `grouping_mark` to "."?

An error is provided when the `decimal_mark` and `grouping_mark` arguments are the same:

```{r}
locale(decimal_mark = ".", grouping_mark = ".")
```

We first print the defaults:

```{r}
locale()
```

If the `decimal_mark` is set to the `,`, then the `grouping_mark` is changed to `.`.

```{r}
locale(decimal_mark = ",")
```

The same happens when the `grouping_mark` is set to `.`:

```{r}
locale(grouping_mark = ".")
```

3.  I didn't discuss the `date_format`and `time_format`options to `locale()`. What do they do? Construct an example that shows when they might be useful.

-   `date_format` and `time_format` are the default formats in the `locale()` function. Both are useful when guessing the format of a vector - i.e. when using the `parse_guess()` function. The defaults are useful date and time parses, respectively.

```{r}
parse_guess('01/31/2013')

parse_guess('17:55:30')
```

4.  If you live outside the US, create a new locale object that encapsulates the settings for the types of file you read most commonly.

```{r}
mx_locale <- locale(date_names = "es")
mx_locale

mx_locale_2 <- locale(date_names = date_names(
  mon = c(
    'enero',
    'febrero',
    'marzo',
    'abril',
    'mayo',
    'junio',
    'julio',
    'agosto',
    'septiembre',
    'octubre',
    'noviembre',
    'diciembre'
  ),
  mon_ab = c('ene',
             'feb',
             'mar',
             'abr',
             'may',
             'jun',
             'jul',
             'ago',
             'sep',
             'oct',
             'nov',
             'dic'),
  day = c('domingo',
          'lunes',
          'martes',
          'miércoles',
          'jueves',
          'viernes',
          'sábado'),
  day_ab = c('dom',
             'lun',
             'mar',
             'mie',
             'jue',
             'vie',
             'sab'),
  am_pm = c("AM", "PM"), date_name))

mx_locale_2

# Now parse strings as date and datetimes with mx_locale_2

parse_date('feb-05-2020', # no period after 'feb' so using mx_locale_2
           format =  "%b-%d-%Y",
           locale = mx_locale_2)

parse_datetime('feb.-05-19-05:10', # period after 'feb', using mx_locale
               format ="%b-%d-%y-%h:%M",
               locale = mx_locale)
```

5.  What's the difference between `read_csv()` and `read_csv2()`?

    `read_csv()` uses `grouping_mark = ","` and `decimal_mark = "."` (like Americans do). On the other hand, `read_csv2()` uses `grouping_mark = "."`, and `decimal_mark = ","` and it separates values with a semicolon: `;`

6.  What are the most common encodings used in Europe? What are the most common encodings used in Asia? Do some googling to find out.

7.  Generate the correct format string to parse each of the following dates and times:

```{r}
d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"
```

```{r}
parse_date(d1, format = "%B %d, %Y")
parse_date(d2, format =  "%Y-%b-%d")
parse_date(d3, format = "%d-%b-%Y")
parse_date(d4, format = "%B %d (%Y)")
parse_time(t1, format = "%H%M")
parse_time(t2, format = "%H:%M:%OS %p")
```

## Parsing a file

### Strategy

`readr` uses a heuristic to figure out the type of each column: it reads the first `1,000` rows and uses some (moderately conservative) heuristics to figure out the type of each column. You can emulate this process with a character vector using `guess_parser()`, which returns `readr`'s best guess, and `parse_guess()` which uses that guess to parse the column:

```{r}
guess_parser('2010-10-01')

guess_parser('15:01')

guess_parser(c('TRUE', 'FALSE'))

guess_parser(c("1", "2", "9"))

guess_parser(c("12,352,561"))

parse_guess('2010-10-10') %>% str()
```

We can note that if we had an Excel file with negative numbers formatted with `()`, we would get those parsed as `chr` types. Thus, we would have to substitute the `()` to a `-` (negative sign) in order for the `parse_guess` function to correctly parse them as numbers.

```{r}
parse_guess(c('(24,384)', '283,402'))
parse_guess(c('-24,384', '283,402')) %>% str()
```

For Excel parsing, you can use the `readxl` function `read_excel()`. For cell and column types, see [the documentation here](<https://readxl.tidyverse.org/articles/cell-and-column-types.html>)

### Other strategies

```{r}
challenge2 <- read_csv(file = readr_example("challenge.csv"), 
                       guess_max = 1001)

challenge2 %>% filter(!is.na(y))
```

Sometimes it's easier to diagnose problems if you just read in all the columns as character vectors:

```{r}
cols_spec <- cols(.default = col_character())

challenge2 <- read_csv(file = readr_example("challenge.csv"),
                       col_types = cols_spec)

challenge2
```


```{r}
df <- tribble(
  ~ x,  ~ y,
  "1", "1.21",
  "2", "2.32",
  "3", "4.56"
)

df


df %>% type_convert()
```


The 


```{r}


```

### Writing to a file

You can write data into disk with `readr`'s functions: `write_csv()` and `write_tsv()` (which will write a tab-separated-values file). The advantage of using these functions is that it will always write the ouput:

1. Using UTF-8 encoding for strings.

2. Saving date-times according to the ISO8601 format.

If you want to export to an Excel file, use the function `write_excel_csv()` which tells Excel that you're using the UTF-8 encoding.

There are 4 important arguments to the `write_*()` functions:

* `x`: the data frame to be saved

* `path`: the path where you will be saving the data.

* `na`: which will specify how missing values will be written.

* `append`: which you have to use if you want to append to an existing file.

The downside of writing to a `.csv` or `.tsv` is that the column specification is lost:

```{r}
challenge2

write_csv(challenge2, path = here("data", "challenge2.csv"))
read_csv(here("data", "challenge2.csv"))
```



This makes CSVs a little unreliable for caching interim results—you need to recreate the column specification every time you load in. There are three alternatives:

1. The RDS file format (which store a single `R` object).
2. The `feather` package for storing files in the `feather` format.
3. The `arrow` package which can store files in the columnar `feather` and `parquet` formats.

```{r}
library(arrow)

write_parquet(challenge2, here("data", "challenge2.parquet"))

read_parquet(file = here("data", "challenge2.parquet"))
```

