---
title: "19 Functions"
description: |
  R for Data Science Book
author:
  - name: Alexis Solis
    url: alexis.solisc@gmail.com
    # affiliation: Spacely Sprockets
    # affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 2
    css: "styles.css"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE)

source("D:/01-Data-Science/03-Helper-Scripts/ggplot2_themes.R")
library(tidyverse)
library(usethis)
```

## 19.3.1 Exercises

1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
```

We see that `f1` checks in the `string` variable wether the first `nchar(prefix)` characters match with the `prefix` string. It should return `TRUE` if true or `FALSE` if false.


```{r}
f3 <- function(x, y) {
  
}
```


2. Take a function that you’ve written recently and spend 5 minutes brainstorming a better name for it and its arguments.

We can create a function that extracts all digits from a string.

```{r}
str_digits <- function(string) {
  if (!is.character(string)) {
    ui_stop("You must provide a character string, not any other type.")
  }
  
  
  if (str_detect(string, "\\d", negate = T)) {
    ui_info("The selected string has no digits. Returning NULL character vector.")
    digits <- NULL
  }
  
  digits <- str_extract_all(string, "\\d") %>% 
    flatten_chr()
  
  return(digits)
}
```


```{r}
str_digits("iojef893289yjkh289439278")
```


3. Compare and contrast `rnorm()` and `MASS::mvrnorm()`. How could you make them more consistent?

```{r}
MASS::mvrnorm()

rnorm()
```

`MASS::mvrnorm()` simulates a multivariate Normal distribution.


4. Make a case for why norm_r(), norm_d() etc would be better than rnorm(), dnorm(). Make a case for the opposite.


# 19.4 Conditional execution

